Information carried by thalamocortical axons enables self-organization of the barrel field

### 2019-11-27 paper/briefpaper/brief.tex
A new figure for the paper

\begin{figure*}
\begin{center}
\includegraphics[width=0.5\textwidth]{../../boundaries/barreloids_haidarliu_graph.png}
\end{center}
%\vspace{-0em}
\caption{Barreloid centres taken from \cite{haidarliu_size_2001} are shown as
  black circles. It is assumed that there are two linearly increasing,
  orthogonal signalling gradients (molecules A \& B) in the thalamus (side
  graphs), such that the location of each barreloid within the graded thalamic
  signal field can differentiate the efferent axons, with the result that
  axons from each barreloid interact to varying degrees with cortical
  signalling gradients. Coloured arrows show, for each barreloid, the
  magnitude (and sign) of the interaction that its thalamocortical projection
  will have with the signalling gradients in the cortex. The mappings from
  barreloid location to interaction strength are linear.}
\label{fig:barreloids}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{../longpaper/realistic_barrels.png}
\end{center}
%\vspace{-0em}
\caption{Realistic barrel pattern}
\label{fig:barrels}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{./MainFig.png}
\end{center}
%\vspace{-0em}
\caption{A. Barreloid centres taken from \cite{haidarliu_size_2001} are shown as
  black circles. It is assumed that there are two linearly increasing,
  orthogonal signalling gradients (molecules A \& B) in the thalamus (side
  graphs), such that the location of each barreloid within the graded thalamic
  signal field can differentiate the efferent axons, with the result that
  axons from each barreloid interact to varying degrees with cortical
  signalling gradients. Coloured arrows show, for each barreloid, the
  magnitude (and sign) of the interaction that its thalamocortical projection
  will have with the signalling gradients in the cortex. The mappings from
  barreloid location to interaction strength are linear. B. }
\label{fig:main}
\end{figure*}
